---
title: "Week 8 R Quiz"
author: "dan berko"
date: "July 25, 2014"
output: html_document
---

Illustrate how to add element by element the contents of two numeric vectors of equal length using a for loop. Comment on how this differs from the easier vector addition method preferred in R.

```{r, addElements}
a = c(1, 3, 5, 7)
b = c(2, 4, 6, 8)
d = vector('integer', 4)
for(x in 1:length(a)){
  d[x] <- a[x] + b[x]
}
d

```
The for loop is much more verbose and doesn't take advantage of the nature of R's vectors.
```{r, convAdd}
a <- c(1, 3, 5, 7)
b <- c(2, 4, 6, 8)
d <- a+b
d
```

Write code that uses a while loop that determines how many "heads" in a row an arbitrary vector of coin flips has starting at the beginning. An example of a vector input is c("heads","heads","tails","heads"). Your code should give an answer of 2 when run on this vector. Note that a vector that begins with "tails" should give an answer of 0.

```{r, NoHeadsInARow}
heads <- 0
count <- 1
flips <- c("tails","heads")
while('heads' == flips[count]){
  heads <- heads + 1
  count <- count + 1
}
heads
```
```{r, 2HeadsInARow}
heads <- 0
count <- 1
flips <- c("heads","heads","tails","heads")
while('heads' == flips[count]){
  heads <- heads + 1
  count <- count + 1
}
heads
```
```{r, 6HeadsInARow}
heads <- 0
count <- 1
flips <- c("heads","heads","heads","heads","heads","heads","tails","heads")
while('heads' == flips[count]){
  heads <- heads + 1
  count <- count + 1
}
heads
```
Use a for loop running over all 100 integers from 1 to 100 and the ifelse() function to add only the odd numbers from 1 to 100. BONUS: Can you show how to accomplish the same thing without using a loop?

```{r,ifelse}

odd <- 0
for ( x in 1:100 ){
  odd = ifelse(x %% 2, odd + x, odd + 0 )
}
odd
```
```{r,ifelsesequece}
x <- (1:100 )
odd = sum(ifelse(x %% 2, x, 0 ))
odd
```